---
title: "Loads Spatial Data Sets Related to China"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geocn}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##"
)
```

The [**geocn**](https://github.com/SpatLyu/geocn) package provides various commonly used spatial data related to Chinese regions in the R programming environment. This vignette presents a quick intro to **geocn**.

### Available data sets

The **geocn** package covers 19 spatial data sets, including a variety of relevant data from both the global and Chinese regions. You can view what data sets are available using the `list_geocn()` function.

```{r}
library(sf)
library(geocn)

datasets_geocn = list_geocn()
datasets_geocn
```

### Region-specific CRS Transformation in China

This section primarily focuses on the conversion between the GCJ02, BD09, and WGS84 coordinate systems. The **geocn** provides `st_transform_cn()` function to achieve the conversion. You need to input the longitude and latitude coordinate vectors to be transformed as function parameters `lon` and `lat`, and specify the CRS before transformation and the CRS to be transformed. Please note that in the `st_transform_cn()` function, the `from` and `to` parameters respectively refer to `wgs`, `gcj`, `bd` for `WGS84`, `GCJ02`, `BD09` coordinate systems. Default Conversion from GCJ02 to WGS84.

```{r}
lon = c(126.626510,126.625261,126.626378,126.626541,126.626721,126.627732,126.626510)
lat = c(45.731596,45.729834,45.729435,45.729676,45.729604,45.730915,45.731596)
st_transform_cn(lon,lat)
```

